---
title: "Data Incubator Finalist Interview"
author: "Yue Jin"
date: "May 14, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = FALSE)
require(ggplot2)
require(dplyr)
```



- App brief

    - Function: XXXXX

- Motivation:

    - 
    - I love craft beer 
    

- Market potential 

    - Competitive analysis
    
    - Market demand

- Dataset
 
 
 
- Subset descriptive data demostration
 
 
 - Algorithm
 
 - Demo: 
 
     - Python Surprise [package](http://surprise.readthedocs.io/en/stable/index.html); SVD matrix factorization
     
     - Test run dataset description: XXXXX
     
     - Test run result
 
 - Algorithm Future Improvement:
 
     - Text feature extracted from textual comments
     
     - More features: user feature, beer feature 
     
     - Popularity based / content based
  
  
- Additional functions:

    - Beer food pairing recommendation
  
     
 - Potential challenges:
 
    - Handle and store big datasets
     
    - Real time update from BeerAdvocate.com
    
    - Front-end design



```{r eda1}
beer<-read.csv("data_scraping_cleaning/top_rated/summary_by_beer_combined.csv")
by_style<-beer %>% group_by(style_name) %>% summarise("n"=n(),"sub_cat"=sub_cat[1]) %>% arrange(desc(n))
by_style<-by_style[1:15,]

p1<-ggplot(data=by_style,aes(x=reorder(style_name,-n),y=n,fill=sub_cat))+
  geom_bar(stat="identity")+
  theme(axis.text.x = element_text(angle = 75, hjust = 1))
p1<-p1+xlab("Beer Style")+ylab("# of Beers")
p1<-p1+labs(fill="Style Category")
p1<-p1+ggtitle("Top 15 styles among Most Rated Beers")+theme(plot.title = element_text(hjust = 0.5))
p1

```

```{r eda2}
company<-read.csv("data_scraping_cleaning/top_rated/summary_by_company.csv")
by_region<-company %>% group_by(region) %>% summarise("n"=sum(n_selected_beers)) %>% arrange(desc(n))
by_region<-by_region[1:15,]
by_region$is_usa<-sapply(by_region$region,substr,1,3)
by_region[by_region$is_usa!="USA",]$is_usa<-"Non-USA"

p2<-ggplot(data=by_region,aes(x=reorder(region,-n),y=n,fill=is_usa))+
  geom_bar(stat="identity")+
  theme(axis.text.x = element_text(angle = 75, hjust = 1))
p2<-p2+xlab("Region")+ylab("# of Beers")
p2<-p2+labs(fill="")
p2<-p2+ggtitle("Top 15 Manufacture Region among Most Rated Beers")+theme(plot.title = element_text(hjust = 0.5))
p2
```
```{r eda3}
by_ava<-beer %>% group_by(availabilities) %>% summarise("n"=n()) %>%
  arrange(desc(n))

by_ava[by_ava$availabilities=="",]$availabilities="N/A"

p3<-ggplot(data=by_ava,aes(x=reorder(availabilities,-n),y=n))+
  geom_bar(stat="identity",fill="steelblue")+
  theme(axis.text.x = element_text(angle = 75, hjust = 1))
p3<-p3+xlab("Availability Type")+ylab("# of Beers")
p3<-p3+ggtitle("Availability of Most Rated Beers")+theme(plot.title = element_text(hjust = 0.5))
p3
```

```{r eda4}
p4<-ggplot(data=beer,aes(scores))+geom_histogram(binwidth = 0.2,color="white",fill="steelblue")
p4<-p4+xlab("BA Score (1.0-5.0)")+ylab("# of Beers")
p4<-p4+ggtitle("BA Score Histogram of Most Rated Beers")+theme(plot.title = element_text(hjust = 0.5))
p4
```

