---
title: "Data Incubator Project Proposal - Plot 2"
author: "Yue Jin"
date: "April 30, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = FALSE)
require(ggplot2)
```

Note: data scraping detail can be found [here](https://github.com/yjin910517/data_incubator/blob/master/data_scraping_cleaning/data_scraping.html). Data cleaning detail can be found [here](https://github.com/yjin910517/data_incubator/blob/master/data_scraping_cleaning/style_data_cleaning.R). Source code in rmd of this plot can be found [here](https://github.com/yjin910517/data_incubator/blob/master/plot2.Rmd)

### Plot #2
```{r p2}
brewery<-read.csv("data_scraping_cleaning/company.csv")
brewery<-brewery[,c(-1,-7)]
brewery$beer_currents<-as.numeric(as.character(brewery$beer_currents))
brewery$total_reviews<-as.numeric(as.character(brewery$total_reviews))
brewery$total_ratings<-as.numeric(as.character(brewery$total_ratings))
brewery$review_per_prod<-brewery$total_reviews/brewery$beer_currents

ba_level<-levels(brewery$ba_levels)
brewery$ba_levels<-factor(brewery$ba_levels,c(ba_level[c(9,6,3,8,4,5,7,2)],"No Rating"))
brewery[is.na(brewery$ba_levels),]$ba_levels<-"No Rating"
brewery<-subset(brewery,!is.na(review_per_prod))

p2<-ggplot(data=brewery,aes(y=review_per_prod,x=beer_currents,color=ba_levels))+geom_point(alpha=0.5)+facet_wrap(~ba_levels)
p2<-p2+ylim(0,200)+xlab("Total Number of Products")+ylab("Average Reviews per Product")+labs(color="BA Rating")
p2<-p2+ggtitle("Summary of 13564 Breweries Worldwide")+theme(plot.title = element_text(hjust = 0.5))
p2
```

#### Description

- Total number of products produced by each brewery shows a long tail pattern, most breweries only produce a small variety of products (mean = 14.39, median = 8), but a few breweries have product line as large as 200+ products

- Breweries with large product line are more likely to get "above average" rating (Exceptional to Good), while outstanding breweries tend to focus on fewer products

- The average review per product is generally low among extreme BA ratings (Awful/World-Class). The rating may not be reliable due to small review size


-----------------
*Definition of BA rating*

- 4.50 - 5.00 = World-Class

- 4.25 - 4.49 = Outstanding

- 4.00 - 4.24 = Exceptional

- 3.75 - 3.99 = Very Good

- 3.50 - 3.74 = Good

- 3.00 - 3.49 = Okay

- 2.00 - 2.99 = Poor

- 1.00 - 1.99 = Awful

