---
title: "Data Incubator Project Proposal - Plot 1"
author: "Yue Jin"
date: "April 30, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning=FALSE)
require(ggplot2)
```

### Plot #1
```{r p1}
styles<-read.csv("data_scraping_cleaning/styles_summary.csv")
p1<-ggplot(data=styles,aes(x=avg_abv,y=avg_rating,color=cat,size=num_beer))
p1<-p1+geom_jitter(alpha=0.8)
p1<-p1+xlab("Average abv (%)")+ylab("Average Rating (0-5)")+ylim(2.0,5.0)
p1<-p1+labs(color="Style Category",size="# of Product Within Style")
p1<-p1+ggtitle("Summary of 104 Beer Styles")+theme(plot.title = element_text(hjust = 0.5))
p1
```

#### Description

All 104 types of beer styles listed on [BeerAdvocate](https://www.beeradvocate.com/beer/style/) were explored in this summary plot. 

There are 4 dimensions of this plot:

- Color: which large category the style belongs to

- Size of Circle: total number of beer products within each style

- X axis: the average alcohol by volume of each style

- y axis: the average rating the style received on BeerAdvocate (0 is the worst, 5 is the best)

------------------------

Following patterns can be observed:

- There are more ale styles than lager styles, and hybrid is the least common one

- In general, ale styles receive higher ratings than lager

- For ale, a positive association can be observed between alc and rating

- Ale styles tend to have a wider range of alc. For lager, most styles have an average alc around 5%, although a few lager styles have much higher alc

- Ale styles are more popular among beer manufacturers (i.e more products), 

